### 2013-03-28 doc/sosp13/method.tex
method: Clean up BFS and add IntSort metric.

\vspace{0.5ex}
\noindent{\bf Breadth-first-search (BFS):} This is the primary kernel for the
Graph500 benchmark and is what currently determines the ranking of machines on
the Graph500 list~\cite{graph500list}. As a whole, the Graph500 benchmark
suite is designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network understanding
workloads. The BFS benchmark builds a search tree containing parent nodes for
each traversed vertex during the search. While this is a relatively simple
problem to solve, it exercises the random-access and fine-grained
synchronization capabilities of a system as well as being a primitive in many
other graph algorithms. Performance is measured in \emph{traversed edges per
second\/} (TEPS), where the number of edges is the edges making up the
generated BFS tree. One of the reference implementations of Graph500 BFS is
for the XMT; this code fails to scale past 16 XMT processors because it does
not expose enough parallelism, so we modified the code to use a recursive loop
decomposition similar to \Grappa's. We compare this modified version against a
straightforward \Grappa implementation. We do not employ algorithmic
improvements, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}.

@@

>>>>

\vspace{0.5ex}
\noindent{\bf Breadth-first-search (BFS):} This is the primary kernel for the
Graph500 benchmark and is what currently determines the ranking of machines on
the Graph500 list~\cite{graph500list}. As a whole, the Graph500 benchmark
suite is designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network understanding
workloads. The BFS benchmark builds a search tree containing parent nodes for
each traversed vertex during the search. While this is a relatively simple
problem to solve, it exercises the random-access and fine-grained
synchronization capabilities of a system as well as being a primitive in many
other graph algorithms. Performance is measured in \emph{traversed edges per
second\/} (TEPS), where the number of edges is the edges making up the
generated BFS tree. With some modifications to the XMT reference version of Graph500 BFS,
the XMT compiler can be made to recognize and apply a Manhattan loop collapse, exposing enough parallelism to allow it to scale out to 64 nodes for the problem scales we show.
We do not employ algorithmic improvements for any of these versions, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}. \Grappa can be expected to benefit the same as MPI due to decreased communication.

@@

The performance metrics for NAS Parallel Benchmarks, including IntSort, are ``millions of operations per second'' (MOPS). For IntSort, this ``operation'' is ranking a single key, so it is roughly comparable to ``GUPS'' or ``TEPS''.
